---
title: "homework4"
author: "mingyue hu"
date: "10/19/2022"
output:
  word_document: default
  pdf_document: default
---



###  Part 1
#Question 1(a)
```{r}
mydat<-read.csv("Kids1.csv")
y<-mydat$oxy
plot(mydat$bm,mydat$oxy)
oxyC<-cut(y,breaks = quantile(y,prob=c(0,seq(0.1,1,by=0.1))),include.lowest=TRUE)
GroupMean<-tapply(y,oxyC,mean)
GroupSD<-tapply(y, oxyC, sd)
lm<-lm(log(GroupSD)~log(GroupMean))
summary(lm)
plot(log(GroupMean),log(GroupSD))
abline(a=coef(lm)[1],b=coef(lm)[2])
```
Ans: The Gamma distribution is chosen for random model component.
The Mean-Variance relationship will be checked in order to choose a random model component. The Box-Cox plot suggests that the coefficient between log(sd) and log(mean) is about 1. Therefore, the Gamma distribution with may be reasonable.

#Question 3
```{r}
plot(mydat$bm,sqrt(mydat$oxy),xlab = "body mass",ylab = "square root of oxy")
plot(mydat$bm,log(mydat$oxy),xlab = "body mass",ylab = "log oxy")
```
Ans: The log link is chosen as the link function. 
After checking the new scatterplot, an approximate linear trend could be observed.

#Question 4
```{r}
gammafit<-glm(mydat$oxy~mydat$bm,family = Gamma(link = "log"))
summary(gammafit)

estse <-as.vector(t(summary(gammafit)$coefficients[,c(1,2)]))
round(estse,4)
#scaled
summary(gammafit)$deviance/summary(gammafit)$dispersion
#unscaled
summary(gammafit)$deviance

intgamma <- cbind(summary(gammafit)$coefficients[,c(1)]-1.96*summary(gammafit)$coefficients[,c(2)],summary(gammafit)$coefficients[,c(1)] +1.96*summary(gammafit)$coefficients[,c(2)])
intgamma

W <- gammafit$weights
X <- cbind(1, mydat$bm)
Z <- sqrt(diag(W))%*%X
H <- Z%*%solve(t(Z)%*%Z)%*%t(Z)
dprime <- residuals(gammafit, type ="deviance")/sqrt(summary(gammafit)$dispersion)/sqrt(1-diag(H))
plot(log(gammafit$fitted), dprime, xlab = "log (Fitted Value)", ylab = "Standardized Deviance Residual"); abline(h=0)

plot(mydat$bm,mydat$oxy)
lines(mydat$bm[order(mydat$bm)],gammafit$fitted.values[order(mydat$bm)])

```


###  Part 2
#Question 1
```{r}

Xmat <- cbind(1, (1:50)/50)
b<-c(-0.5,2)
mydat<-rbinom(50,1,prob = 1-exp(-exp((Xmat)%*%b)))
Xmat<-data.frame(Xmat)
plot(Xmat$X2,mydat)
```



#Question 2
```{r}
fit<-glm(mydat~Xmat$X2,family = binomial(link = "cloglog"))
summary(fit)

int <- cbind( summary(fit)$coefficients[,c(1)] - 1.96*summary(fit)$coefficients[,c(2)] ,
summary(fit)$coefficients[,c(1)] +1.96*summary(fit)$coefficients[,c(2)])
int

#scaled
summary(fit)$deviance/summary(fit)$dispersion
#unscaled
summary(fit)$deviance

ests<-predict(fit,se.fit = TRUE,type = "response")
bhat<-as.numeric(coef(fit))
Xmat <- cbind(1, (1:50)/50)
phat = 1-exp(-exp((Xmat)%*%bhat))
likeli<-t(log(phat))%*%mydat+t(log(1-phat))%*%(1-mydat)
likeli

Xmat <- cbind(1, (1:50)/50)
prob = 1-exp(-exp((Xmat)%*%b))
Xmat<-data.frame(Xmat)
plot(Xmat$X2,mydat)
lines(Xmat$X2[order(Xmat$X2)],ests$fit[order(Xmat$X2)])
lines(Xmat$X2,prob,lty=2)
```


#Question 3
```{r}
ests<-predict(fit,se.fit = TRUE,type = "response")
lower<-ests$fit-1.96*ests$se.fit
upper<-ests$fit+1.96*ests$se.fit

Xmat<-data.frame(Xmat)
plot(Xmat$X2,mydat)
lines(Xmat$X2[order(Xmat$X2)],ests$fit[order(Xmat$X2)])
lines(Xmat$X2[order(Xmat$X2)],lower[order(Xmat$X2)],lty=2)
lines(Xmat$X2[order(Xmat$X2)],upper[order(Xmat$X2)],lty=2)
```



### part 3
```{r}
data<-read.csv("CloudData.csv")
data1<-data.frame(matrix(data=c(data$UnseededRain,data$SeededRain),ncol = 1))
colnames(data1)<-"Rain"
data1$seed<-c(rep(0,26),rep(1,26))
glmfit <- glm(data1$Rain~as.factor(data1$seed)-1,family = Gamma(link = "identity"))
summary(glmfit)

intglm <- cbind(summary(glmfit)$coefficients[,c(1)]-1.96*summary(glmfit)$coefficients[,c(2)],summary(glmfit)$coefficients[,c(1)] +1.96*summary(glmfit)$coefficients[,c(2)])
intglm

```








